Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2024-08-07 analysis/paper/paper.Rmd
Fix some scale in figures

mod_list <- list(
  pp_check(m_f1, type = "bars", ndraws = 50) +
    scale_x_continuous(,
                       breaks = c(1, 2, 3, 4),
                       limits = c(0.5, 4.5)) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_f2, type = "bars", ndraws = 50) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ),
  pp_check(m_g1, type = "bars", ndraws = 50) +
    scale_x_continuous(,
                       breaks = c(1, 2, 3, 4),
                       limits = c(0.5, 4.5)) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_g2, type = "bars", ndraws = 50) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ),
  pp_check(m_h1, type = "bars", ndraws = 50) +
    scale_x_continuous(
      labels = c("0", "1", "2", "3"),
      breaks = c(1, 2, 3, 4),
      limits = c(0.5, 4.5)
    ) +
    xlab("Score (0 to 3)"),
  pp_check(m_h2, type = "bars", ndraws = 50) +
    scale_x_continuous(labels = c("0", "1", "2", "3"),
                       breaks = c(1, 2, 3, 4),
                       limits = c(0.5, 4.5)) +
    xlab("Score (0 to 3)") +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    )
)

>>>>

mod_list <- list(
  pp_check(m_f1, type = "bars", ndraws = 50) +
    scale_x_continuous(
      labels = c("0", "1", "2", "3"),
      breaks = c(1, 2, 3, 4),
      limits = c(0.5, 4.5)
    ) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_f2, type = "bars", ndraws = 50) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ),
  pp_check(m_g1, type = "bars", ndraws = 50) +
    scale_x_continuous(
      labels = c("0", "1", "2", "3"),
      breaks = c(1, 2, 3, 4),
      limits = c(0.5, 4.5)
    ) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank()
    ),
  pp_check(m_g2, type = "bars", ndraws = 50) +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ),
  pp_check(m_h1, type = "bars", ndraws = 50) +
    scale_x_continuous(
      labels = c("0", "1", "2", "3"),
      breaks = c(1, 2, 3, 4),
      limits = c(0.5, 4.5)
    ) +
    xlab("Score (0 to 3)"),
  pp_check(m_h2, type = "bars", ndraws = 50) +
    scale_x_continuous(
      labels = c("0", "1", "2", "3"),
      breaks = c(1, 2, 3, 4),
      limits = c(0.5, 4.5)
    ) +
    xlab("Score (0 to 3)") +
    theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    )
)
